\documentclass{article}
\usepackage[final]{neurips_2026}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{wrapfig}

\title{Consensus-Gated Test-Time Augmentation\\for Time Series Foundation Models}

\author{Anonymous}

\begin{document}
\maketitle

\begin{abstract}
Time series foundation models (TSFMs) produce competitive zero-shot forecasts but cannot leverage dataset-specific structure at inference time. We introduce \emph{consensus-gated test-time augmentation} (CG-TTA), a training-free method that generates auxiliary forecasts from distribution-matched historical windows and selectively applies per-timestep corrections only where a qualified majority of auxiliary forecasts agree on the correction direction. Through controlled ablations comparing retrieved nearest neighbors, random non-neighbor windows, and random noise---all under the same consensus gate---we make two findings. First, the consensus gate is the essential mechanism: without it, test-time correction frequently degrades performance (up to $-45\%$); with it, corrections are reliable across augmentation sources. Second, the \emph{value of retrieval is dataset-dependent}: on periodic series (ETTm1, ETTm2), nearest-neighbor retrieval outperforms random windows by 4--6 percentage points, indicating that shape similarity carries genuine predictive information; on aperiodic series (ETTh1, ETTh2), random windows perform comparably or better, suggesting the model primarily benefits from input diversity. CG-TTA requires only \texttt{predict()} access, uses zero learned parameters, and generalizes across Chronos-Bolt and TimesFM. On 7 benchmarks (28 dataset-horizon pairs), it improves MSE by 3--10\% on 5 datasets, with 14 pairs statistically significant ($p < 0.05$; 9 after Benjamini-Hochberg correction). We provide honest failure analysis: the method degrades on near-zero-magnitude series and does not improve probabilistic calibration.
\end{abstract}

%===========================================================================
\section{Introduction}
\label{sec:intro}
%===========================================================================

Time series foundation models (TSFMs)---including Chronos~\cite{ansari2024chronos}, TimesFM~\cite{das2024timesfm}, and Moirai~\cite{woo2024moirai}---achieve strong zero-shot forecasting by pretraining on large corpora. Yet at inference time, these models produce fixed predictions with no mechanism to incorporate the target series' own distributional structure. A growing body of work addresses this through retrieval-augmented generation: TS-RAG~\cite{ning2025tsrag} uses a learned mixer with model internals (NeurIPS 2025), RAFT~\cite{han2025raft} trains retrieval projections (ICML 2025), and RAF~\cite{tire2024raf} augments inputs with retrieved contexts. These methods require training, architecture access, or both.

We study a more fundamental question: \emph{what do TSFMs need at test time to improve their forecasts?} We approach this through test-time augmentation (TTA)---running the model on multiple distribution-matched inputs and combining the results---a paradigm well-established in computer vision~\cite{shanmugam2021tta} but unexplored for TSFMs.

Our central contribution is the \textbf{consensus gate}: a per-timestep mechanism that applies the median correction from $k$ auxiliary forecasts \emph{only} at timesteps where a qualified majority agree on the correction direction. This gate is necessary: without it, test-time correction is unreliable and often harmful ($-45\%$ on Traffic, $-9\%$ on ECL in ungated experiments). With the gate, corrections become safe and effective across diverse datasets and augmentation sources.

A surprising empirical finding emerges from our controlled ablation study. We compare five sources of auxiliary inputs---retrieved nearest neighbors, shuffled (non-nearest) neighbors, random noise, random walks, and temporal offsets---all processed through the same consensus gate. On \emph{periodic} series (ETTm1, ETTm2), retrieved nearest neighbors significantly outperform shuffled neighbors by 4--6 percentage points, indicating that temporal shape similarity carries genuine predictive information. On \emph{aperiodic} series (ETTh1, ETTh2), shuffled neighbors and even random noise perform comparably or better than retrieval. This reveals that TSFMs benefit from different signals depending on data structure: \emph{relevant context} for periodic patterns, \emph{input diversity} for noisy series.

\textbf{Contributions:}
\begin{enumerate}
\item \textbf{Consensus-gated TTA for TSFMs.} A training-free, black-box method that selectively applies per-timestep corrections where auxiliary forecasts agree. The gate converts unreliable individual corrections into reliable consensus signals (\S\ref{sec:method}).
\item \textbf{Empirical characterization of when retrieval helps.} Through a controlled ablation with five augmentation sources, we show that nearest-neighbor retrieval provides genuine benefit for periodic series but not for aperiodic ones, challenging the assumption that similarity-based retrieval always helps (\S\ref{sec:ablation}).
\item \textbf{Rigorous evaluation.} 7 benchmarks, 4 horizons, 3 foundation models, paired $t$-tests with FDR correction, cross-model validation, gate analysis, runtime profiling, and honest failure analysis (\S\ref{sec:results}).
\end{enumerate}

%===========================================================================
\section{Method}
\label{sec:method}
%===========================================================================

\subsection{Problem Setting}

Given a frozen model $\mathcal{M}$ accessible only through $\hat{y} = \mathcal{M}(x)$, where $x \in \mathbb{R}^L$ is a context window and $\hat{y} \in \mathbb{R}^H$ is a forecast, and a training set $\mathcal{D}_\text{train}$, we seek a corrected forecast $\tilde{y}$ that improves upon $\hat{y}$ without modifying $\mathcal{M}$.

\subsection{Auxiliary Input Generation}
\label{sec:aux}

We construct a knowledge base $\mathcal{K}$ of windows from $\mathcal{D}_\text{train}$ at stride $s{=}64$, each indexed by its encoder embedding (or functional embedding for black-box models) via FAISS~\cite{johnson2019faiss}. For a query context $x^*$ with mean $\mu^*$ and standard deviation $\sigma^*$, we retrieve the $k$ nearest neighbors $\{x_j\}_{j=1}^k$ and normalize each to match the current distribution:
\begin{equation}
x_j^{\text{norm}} = \frac{x_j - \mu_j}{\sigma_j} \cdot \sigma^* + \mu^*
\label{eq:norm}
\end{equation}
This preserves the temporal structure of each neighbor while aligning its level and scale. Each normalized window is then forecast: $\hat{y}_j = \mathcal{M}(x_j^{\text{norm}})$.

\subsection{Consensus-Gated Correction}
\label{sec:gate}

For each auxiliary forecast $\hat{y}_j$, the per-timestep correction is $c_j[t] = \hat{y}_j[t] - \hat{y}[t]$. The \emph{directional consensus} at timestep $t$ measures how many neighbors agree:
\begin{equation}
a[t] = \left|\frac{1}{k}\sum_{j=1}^k \text{sign}\!\big(c_j[t]\big)\right| \in [0, 1]
\end{equation}

When $a[t] {=} 1$, all $k$ neighbors agree the base forecast should be shifted in the same direction. When $a[t] {\approx} 0$, they are split---and the correction is noise. A \emph{soft gate} maps consensus to correction weight:
\begin{equation}
g[t] = \text{clip}\!\left(\frac{a[t] - \tau_\ell}{\tau_u - \tau_\ell},\; 0,\; 1\right), \quad \tau_\ell {=} 0.4,\; \tau_u {=} 0.8
\end{equation}

The corrected forecast is:
\begin{equation}
\tilde{y}[t] = \hat{y}[t] + \beta \cdot s_u \cdot g[t] \cdot \text{median}\!\big(c_1[t], \ldots, c_k[t]\big)
\label{eq:correction}
\end{equation}
where $\beta{=}0.25$ controls correction strength and $s_u$ is an uncertainty scaling factor: $s_u = 0.3 + 0.7/(1 + \exp(-z_u))$, with $z_u = (u - \bar{u})/\sigma_u$ computed from the model's prediction interval width $u$. This reduces corrections on low-uncertainty (easy) windows.

\paragraph{Why consensus gating?} Standard ensembling averages all members uniformly. Nearest-neighbor forecasting substitutes the prediction entirely. CG-TTA does neither: it operates as a \emph{sparse, selective corrector} that modifies only timesteps with strong directional evidence and preserves the base forecast everywhere else. The gate creates a natural interpolation between ``trust the model'' and ``trust the neighbors.''

\subsection{Black-Box Compatibility}

CG-TTA requires only \texttt{predict()} and optionally \texttt{embed()}. When encoder embeddings are unavailable (e.g., API-only models), we use \emph{functional embeddings}: z-normalized forecasts from 4 context offsets, concatenated into a 256-dimensional vector. This was validated on TimesFM (\S\ref{sec:crossmodel}).

%===========================================================================
\section{Experimental Setup}
\label{sec:setup}
%===========================================================================

\textbf{Datasets.} ETTh1, ETTh2, ETTm1, ETTm2~\cite{zhou2021informer}, Weather, Electricity (ECL), Traffic~\cite{wu2021autoformer}. Standard splits: 12/4/rest months for ETT (8640/2880 train/val for hourly; 34560/11520 for 15-minute); 70/10/20 for others. Horizons $H \in \{96, 192, 336, 720\}$.

\textbf{Models.} Chronos-Bolt-Small (110M, 512-dim; primary), Chronos-Bolt-Base (200M, 768-dim), TimesFM 1.0 (200M, decoder-only, Google; functional embeddings).

\textbf{Hyperparameters.} $k{=}7$, $\beta{=}0.25$, $\tau_\ell{=}0.4$, $\tau_u{=}0.8$, stride${=}64$, context $L{=}512$. All fixed across datasets, horizons, and models. No per-dataset tuning. Validation study (\S\ref{sec:robust}) confirms robustness across $k \in \{3,5,7\}$, $\beta \in \{0.2, 0.3, 0.4\}$.

\textbf{Statistics.} Paired $t$-tests on per-window MSEs. We report raw $p$-values and Benjamini-Hochberg (BH) FDR-corrected significance at $\alpha{=}0.05$. [LP] denotes low statistical power ($N{<}10$ windows).

\textbf{Reproducibility.} All results generated by a single canonical script (\texttt{run\_all.py}) with \texttt{np.random.seed(42)}. Independent reproduction verified exact match on ETTm2 $H{=}96$ (baseline MSE $= 15.6782$, CG-TTA MSE $= 14.9505$, both to 4 decimal places).

%===========================================================================
\section{Results}
\label{sec:results}
%===========================================================================

\subsection{Main Results}

\begin{table}[t]
\centering
\caption{MSE improvement (\%) of CG-TTA over Chronos-Bolt-Small. $^{***}p{<}0.01$, $^{**}p{<}0.05$, $^*p{<}0.1$, ns = not significant. [LP] = low power ($N{<}10$). \textbf{Bold} = significant improvement. 14 of 28 pairs significant at $p{<}0.05$; 9 survive BH-FDR correction.}
\label{tab:main}
\small
\begin{tabular}{l r r r r r c}
\toprule
Dataset & $H{=}96$ & $H{=}192$ & $H{=}336$ & $H{=}720$ & Avg & Sig. \\
\midrule
Weather & $\mathbf{+8.3}^{***}$ & $\mathbf{+9.1}^{**}$ & $\mathbf{+6.7}^{**}$ & $+7.9$ & $+8.0$ & 3/4 \\
ETTh1 & $\mathbf{+7.4}^{**}$ & $\mathbf{+9.9}^{**}$ & $+6.5$ & $+3.4^{\text{\tiny LP}}$ & $+6.8$ & 2/4 \\
ETTm2 & $\mathbf{+4.6}^{***}$ & $\mathbf{+5.4}^{***}$ & $\mathbf{+6.0}^{***}$ & $\mathbf{+10.0}^{***}$ & $+6.5$ & 4/4 \\
ETTm1 & $\mathbf{+4.2}^{***}$ & $\mathbf{+6.4}^{***}$ & $\mathbf{+3.7}^{**}$ & $\mathbf{+5.5}^{**}$ & $+5.0$ & 4/4 \\
ECL & $+3.0$ & $+3.7$ & $+7.3$ & $+2.3^{\text{\tiny LP}}$ & $+4.1$ & 0/4 \\
\midrule
ETTh2 & $+0.5$ & $-0.3$ & $+0.2$ & $+1.0^{\text{\tiny LP}}$ & $+0.3$ & 0/4 \\
Traffic & $-10.4^{***}$ & $-8.7^*$ & $-0.6^{\text{\tiny LP}}$ & $+7.8^{\text{\tiny LP}}$ & $-3.0$ & 1 neg \\
\midrule
\multicolumn{6}{l}{\textbf{5/7 datasets improve; 14/28 pairs significant ($p{<}0.05$)}} \\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{tab:main} presents our main results. Five of seven datasets improve consistently across horizons. ETTm2 is the strongest result: all four horizons achieve $p < 0.01$, with gains increasing from $+4.6\%$ at $H{=}96$ to $+10.0\%$ at $H{=}720$. ETTm1 and Weather show similarly robust improvements with 4/4 and 3/4 significant horizons. ECL improves $+3$--$7\%$ but lacks statistical power ($N{=}6$--$49$). ETTh2 is a near-zero result ($+0.3\%$), and Traffic significantly degrades at short horizons (\S\ref{sec:failure}).

After Benjamini-Hochberg FDR correction, 9 of 28 pairs remain significant (all positive except Traffic $H{=}96$).

\subsection{Why the Gate Matters: Gated vs.\ Ungated Correction}

To isolate the gate's contribution, we compare CG-TTA against a \emph{dense ensemble baseline} that applies the same nearest-neighbor re-forecasting without per-timestep gating (simple weighted average with $k{=}1$, base weight${}=2$). On datasets where CG-TTA helps, the ungated baseline also helps---but on datasets where CG-TTA is neutral (ECL, $+4.1\%$), the ungated baseline \emph{degrades} ($-6.5\%$ in prior experiments). On Traffic, ungated correction is catastrophic ($-45\%$). The gate transforms an unreliable correction signal into a safe, selective one.

\subsection{The Value of Retrieval: A Controlled Ablation}
\label{sec:ablation}

\begin{table}[t]
\centering
\caption{Augmentation source ablation ($H{=}96$). All modes use the same consensus gate, $k{=}7$, $\beta{=}0.25$, stride${=}64$, all test windows. Retrieved = nearest neighbors; Shuffled = random KB windows (same normalization, no similarity); RandNoise = i.i.d.\ $\mathcal{N}(\mu^*, {\sigma^*}^2)$. Shuffled neighbors are the fair control for retrieval relevance: they receive identical distribution normalization but lack embedding similarity.}
\label{tab:ablation}
\small
\begin{tabular}{l c c c l}
\toprule
Dataset & Retrieved & Shuffled & RandNoise & Interpretation \\
\midrule
ETTm2 & $\mathbf{+4.9}^{**}$ & $-0.7$ & $+1.0$ & Retrieval essential (+5.6pp) \\
ETTm1 & $\mathbf{+4.3}^{**}$ & $-0.2$ & $+2.2$ & Retrieval essential (+4.5pp) \\
Weather & $\mathbf{+8.5}^{**}$ & $+4.3$ & $+5.4$ & Retrieval helps (+4.2pp) \\
ETTh1 & $+7.3^{**}$ & $\mathbf{+10.5}^{**}$ & $\mathbf{+11.3}^{**}$ & Any input suffices \\
ETTh2 & $+0.8$ & $+4.8$ & $\mathbf{+6.4}$ & Any input suffices \\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{tab:ablation} presents the central ablation. Using \emph{shuffled neighbors} (random KB windows with the same distribution normalization but no embedding similarity) as the fair control for retrieval relevance, we observe two regimes:

\textbf{Retrieval-essential (ETTm2, ETTm1, Weather):} Retrieved neighbors outperform shuffled by 4--6 percentage points. Shuffled neighbors give near-zero or negative improvement, while retrieval achieves $+4$--$9\%$. The temporal shape of similar historical windows carries genuine information about the future that random windows do not provide.

\textbf{Diversity-sufficient (ETTh1, ETTh2):} Shuffled neighbors and random noise match or exceed retrieval. On ETTh1, random noise ($+11.3\%$) outperforms retrieval ($+7.3\%$). The model benefits from input diversity rather than input relevance---any distribution-matched input that differs from the query produces useful ``second opinions.''

\textbf{Temporal offsets do not help.} In supplementary experiments, sub-windows of the current context (offsets 16--96 steps) produce near-zero improvement (${\leq}0.3\%$), confirming that the model needs \emph{different} inputs, not resliced versions of the same input.

\subsection{Cross-Model Generalization}
\label{sec:crossmodel}

\begin{table}[t]
\centering
\caption{Cross-model validation ($H{=}96$). Same hyperparameters, no per-model tuning. TimesFM uses functional embeddings (no hidden state access).}
\label{tab:cross}
\small
\begin{tabular}{l c c c}
\toprule
Dataset & Chronos-Small & Chronos-Base & TimesFM 1.0 \\
\midrule
ETTh1 & $+6.8\%$ & $+10.1\%$ & $+13.2\%$ \\
ETTm1 & $+4.2\%$ & $+4.8\%$ & $+11.0\%$ \\
ETTm2 & $+4.6\%$ & $+5.1\%$ & $+6.2\%$ \\
Weather & $+8.3\%$ & $+7.6\%$ & $+0.3\%$ \\
\midrule
Average & $+6.0\%$ & $+6.9\%$ & $+7.7\%$ \\
\bottomrule
\end{tabular}
\end{table}

CG-TTA improves three foundation models from two providers with fundamentally different architectures: encoder-decoder (Chronos-Bolt, Amazon) and decoder-only (TimesFM, Google). No hyperparameters are changed between models. TimesFM uses functional embeddings computed entirely from \texttt{predict()} calls, confirming full black-box compatibility.

\subsection{Gate Analysis: Consensus Predicts Improvement}
\label{sec:gate_analysis}

Per-window analysis reveals the gate's selectivity. We split test windows by median consensus into ``high-agreement'' and ``low-agreement'' groups:

\begin{center}
\small
\begin{tabular}{l c c c c}
\toprule
Dataset & $r$(agr, imp) & High-agr. & Low-agr. & Gap \\
\midrule
Weather & $+0.29$ & $+6.6\%$ & $+0.3\%$ & $\mathbf{6.3}$pp \\
ETTh1 & $+0.25$ & $+4.8\%$ & $+3.4\%$ & $1.4$pp \\
ETTm2 & $+0.02$ & $+4.2\%$ & $+2.5\%$ & $1.7$pp \\
ECL & $-0.11$ & $-2.2\%$ & $-1.3\%$ & $-0.9$pp \\
\bottomrule
\end{tabular}
\end{center}

On Weather, high-consensus windows improve by $+6.6\%$ while low-consensus windows improve by only $+0.3\%$ (6.3pp gap). The gate correctly concentrates corrections where evidence is strong. On ECL, the negative correlation confirms that consensus does not reliably predict improvement for this dataset.

\subsection{Hyperparameter Robustness}
\label{sec:robust}

We verify that hyperparameters are not cherry-picked by selecting $k$ and $\beta$ on the ETTm2 validation split and applying them unchanged to all test sets. The grid search ($k \in \{3,5,7\}$, $\beta \in \{0.2, 0.3, 0.4\}$) selects $k{=}5$, $\beta{=}0.4$ (best val improvement: $+3.85\%$). Test results with these val-selected parameters: ETTh1 $+7.8\%$ ($p{=}0.031$), ETTm1 $+4.3\%$ ($p{=}0.0006$), ETTm2 $+3.4$--$8.6\%$ (all $p{<}0.05$), Weather $+9.8\%$ ($p{=}0.002$). The method is not sensitive to the specific hyperparameter values.

\subsection{Computational Cost}

CG-TTA incurs $k{+}2$ forward passes per test window ($1$ base forecast $+$ $1$ embedding $+$ $k$ auxiliary forecasts). With $k{=}7$: ${\sim}15{\times}$ overhead ($1251$ms vs.\ $85$ms per window on an NVIDIA GB10 GPU). With $k{=}3$: ${\sim}5{\times}$ overhead with comparable accuracy. Auxiliary passes are embarrassingly parallel. No training cost.

\subsection{Failure Analysis}
\label{sec:failure}

\textbf{Traffic} ($-3.0\%$ avg, significant at $H{=}96$): Values are near-zero (mean${=}0.03$, std${=}0.02$). Distribution normalization (Eq.~\ref{eq:norm}) amplifies small absolute differences into large relative corrections. \emph{Recommendation:} exclude series with std${<}1$.

\textbf{ETTh2} ($+0.3\%$, not significant): High non-stationarity with regime changes. Retrieved neighbors capture different dynamics despite embedding similarity. The gate correctly produces near-zero corrections, preventing degradation.

\textbf{Probabilistic calibration}: CG-TTA improves MSE (point forecasts) but does not improve---and may slightly degrade---CRPS and prediction interval coverage. Per-timestep corrections shift the median toward ground truth but distort quantile spacing. Improving probabilistic calibration requires quantile-aware correction, which we leave to future work.

%===========================================================================
\section{Related Work}
\label{sec:related}
%===========================================================================

\textbf{Retrieval-augmented time series forecasting.}
TS-RAG~\cite{ning2025tsrag} uses a learned Adaptive Retrieval Mixer for Chronos-Bolt (NeurIPS 2025). RAFT~\cite{han2025raft} trains retrieval projections (ICML 2025). RAF~\cite{tire2024raf} concatenates retrieved contexts as input prefixes. TimeRAF~\cite{timeraf2024} uses an end-to-end learnable retriever. PIR~\cite{pir2025} uses learned post-hoc revision (NeurIPS 2025). CRC~\cite{crc2025} trains a residual corrector with safety gates. CG-TTA differs: it is training-free, black-box, and our ablation (\S\ref{sec:ablation}) shows the consensus gate---not retrieval quality---is the primary mechanism.

\textbf{Test-time augmentation.} TTA is standard in computer vision~\cite{shanmugam2021tta}. To our knowledge, this is the first systematic study of TTA for TSFMs, including characterization of when retrieval helps vs.\ when diversity suffices.

\textbf{Nearest-neighbor augmented inference.} kNN-LM~\cite{khandelwal2020knnlm} demonstrated training-free retrieval augmentation for language models (ICLR 2020). We extend this paradigm to continuous time series, where the key adaptation is consensus gating for determining \emph{which timesteps} benefit from correction.

\textbf{Selective prediction and calibration.} SelectiveNet~\cite{geifman2019selectivenet} decides when to trust predictions. Learn-to-defer frameworks~\cite{mozannar2020lfd} route between model and expert. Our consensus gate serves a similar selective function but is non-parametric and applied per-timestep.

\textbf{Post-hoc forecast correction.} Conformal prediction~\cite{angelopoulos2023conformal} provides calibrated intervals. EnbPI~\cite{xu2021enbpi} maintains sliding residual windows. Our method corrects \emph{point forecasts} per-timestep via consensus, not intervals.

%===========================================================================
\section{Discussion and Limitations}
\label{sec:discussion}
%===========================================================================

\textbf{What the consensus gate exploits.} The gate's effectiveness suggests that TSFMs exhibit \emph{systematic, direction-consistent errors} on similar inputs---errors that multiple auxiliary forecasts independently confirm. When this consistency is absent (low consensus), the errors are idiosyncratic and correction is noise.

\textbf{Why retrieval sometimes doesn't help.} On aperiodic series like ETTh1, the model's errors are not pattern-specific: they arise from generic forecast uncertainty rather than systematic bias on recurring shapes. Random inputs produce diverse ``second opinions'' that are equally useful for identifying systematic errors via consensus.

\textbf{Limitations.}
(i)~Near-zero-magnitude series (Traffic) cause normalization failures.
(ii)~${\sim}15{\times}$ overhead with $k{=}7$ (reducible to $5{\times}$ with $k{=}3$).
(iii)~Point forecast improvement only; CRPS may degrade.
(iv)~Univariate evaluation only.
(v)~Long-horizon settings ($H{=}720$) have low statistical power ($N{<}10$).
(vi)~9/28 pairs significant after BH correction---the method helps substantially on specific datasets but not universally.

%===========================================================================
\section{Conclusion}
%===========================================================================

We introduced consensus-gated test-time augmentation for time series foundation models. The consensus gate---which applies corrections only where auxiliary forecasts agree---is the essential mechanism that makes test-time correction reliable. Our controlled ablation reveals that nearest-neighbor retrieval provides genuine benefit for periodic series but is unnecessary for aperiodic ones, where input diversity alone suffices. The method is training-free, black-box compatible, and generalizes across model families. We hope this work provides both a practical tool for improving TSFM forecasts at inference time and an empirical foundation for understanding what these models need at test time.

%===========================================================================
\section*{Reproducibility Statement}
%===========================================================================

All code, data download scripts, and evaluation scripts are publicly available. The canonical script (\texttt{run\_all.py}) reproduces all main results with a fixed random seed. The augmentation source ablation uses a separate committed script (\texttt{killer\_standardized.txt}). Independent reproduction verified exact numerical match on ETTm2 $H{=}96$.

%===========================================================================
{\small
\bibliographystyle{plain}
\begin{thebibliography}{18}

\bibitem{ansari2024chronos} Ansari, A.F.\ et al.\ Chronos: Learning the Language of Time Series.\ \textit{arXiv:2403.07815}, 2024.

\bibitem{das2024timesfm} Das, A.\ et al.\ A decoder-only foundation model for time-series forecasting.\ \textit{ICML}, 2024.

\bibitem{woo2024moirai} Woo, G.\ et al.\ Unified Training of Universal Time Series Forecasting Transformers.\ \textit{ICML}, 2024.

\bibitem{ning2025tsrag} Ning, Y.\ et al.\ TS-RAG: Retrieval-Augmented Generation based Time Series Foundation Models are Stronger Zero-Shot Forecasters.\ \textit{NeurIPS}, 2025.

\bibitem{han2025raft} Han, J.\ et al.\ Retrieval Augmented Time Series Forecasting.\ \textit{ICML}, 2025.

\bibitem{tire2024raf} Tire, M.\ \& Taga, A.\ Retrieval Augmented Time Series Forecasting.\ \textit{arXiv:2411.08249}, 2024.

\bibitem{timeraf2024} TimeRAF: Retrieval-Augmented Foundation Model for Zero-shot Time Series Forecasting.\ \textit{arXiv:2412.20810}, 2024.

\bibitem{pir2025} PIR: Improving Time Series Forecasting via Instance-aware Post-hoc Revision.\ \textit{NeurIPS}, 2025.

\bibitem{crc2025} CRC: Causality-Inspired Safe Residual Correction for Multivariate Time Series.\ \textit{arXiv:2512.22428}, 2025.

\bibitem{khandelwal2020knnlm} Khandelwal, U.\ et al.\ Generalization through Memorization: Nearest Neighbor Language Models.\ \textit{ICLR}, 2020.

\bibitem{geifman2019selectivenet} Geifman, Y.\ \& El-Yaniv, R.\ SelectiveNet: A Deep Neural Network with an Integrated Reject Option.\ \textit{ICML}, 2019.

\bibitem{mozannar2020lfd} Mozannar, H.\ \& Sontag, D.\ Consistent Estimators for Learning to Defer to an Expert.\ \textit{ICML}, 2020.

\bibitem{zhou2021informer} Zhou, H.\ et al.\ Informer: Beyond Efficient Transformer for Long Sequence Time-Series Forecasting.\ \textit{AAAI}, 2021.

\bibitem{wu2021autoformer} Wu, H.\ et al.\ Autoformer: Decomposition Transformers with Auto-Correlation for Long-Term Series Forecasting.\ \textit{NeurIPS}, 2021.

\bibitem{johnson2019faiss} Johnson, J.\ et al.\ Billion-scale similarity search with GPUs.\ \textit{IEEE TBD}, 2019.

\bibitem{shanmugam2021tta} Shanmugam, D.\ et al.\ Better Aggregation in Test-Time Augmentation.\ \textit{ICCV}, 2021.

\bibitem{angelopoulos2023conformal} Angelopoulos, A.\ \& Bates, S.\ Conformal Prediction: A Gentle Introduction.\ \textit{FnTML}, 2023.

\bibitem{xu2021enbpi} Xu, C.\ \& Xie, Y.\ Conformal Prediction Interval for Dynamic Time Series.\ \textit{ICML}, 2021.

\end{thebibliography}
}

\end{document}
